The 18.821 Mathematics Project Lab Report [Proofs]

### 2013-09-28 paper.tex
Including a figure as reference.
Reorganizing the paper. Moving notation into the appendix.

\section{Theorems}

@@

To make a simple model of this problem, we will use a quadrilateral to model a path around a cone. We will construct a quadrilateral with particular constaints that models the constraints of a path around a cone, and we will try to find the parameters that minimize the perimeter around the quadrilateral. Let us call the sides of the quadrilateral $s_1, s_2, s_3$ and $s_4$. Imagine that $s_1$ and $s_2$ are on opposite sides of the quadrilateral with fixed lengths $l_1$ and $l_2$ respectively. Now we will constrain the problem to be related to the problem of a particle traveling around a cone: imagine $s_1$ and $s_2$ are connected by a bar $s_b$ of length $d$. The bar will be perpendicular to $s_1$. The angle that $s_b$ forms with $s_2$ will be called $\theta$. We will try to find the optimal $\theta$ that minimizes the perimeter around the quadrilateral.
\begin{figure}
\end{figure}

@@

>>>>

\section{Introduction}

\section{Background and Definitions}

In this section, we will make some basic definitions about particles and paths. These should lay the groundwork for thinking about optimal paths. We will begin by defining the description of a particle and then define various types of paths that a particle can take.

@@

To make a simple model of this problem, we will use a quadrilateral to model a path around a cone. We will construct a quadrilateral with particular constaints that models the constraints of a path around a cone, and we will try to find the parameters that minimize the perimeter around the quadrilateral. Let us call the sides of the quadrilateral $s_1, s_2, s_3$ and $s_4$. Imagine that $s_1$ and $s_2$ are on opposite sides of the quadrilateral with fixed lengths $l_1$ and $l_2$ respectively. Now we will constrain the problem to be related to the problem of a particle traveling around a cone: imagine $s_1$ and $s_2$ are connected by a bar $s_b$ of length $d$. The bar will be perpendicular to $s_1$. The angle that $s_b$ forms with $s_2$ will be called $\theta$. We will try to find the optimal $\theta$ that minimizes the perimeter around the quadrilateral.

We will use figure \label{fig:quadrilateral} as reference.

\begin{figure}
  \includegraphics[width=3in]{figures/quad.eps}
  \caption{Minimizing perimeter around a quadrilateral}
\end{figure}

@@

\section{Appendix}
